### 2025-11-08 thesis/implementation/index.tex
Fix lang

The heuristic method employed by the voting algorithm is steering the pipeline
to agree with itself – if multiple generation attempts yielded the same result,
these generation attempts are more likely than outliers.

@@

Queries that voting function fails with execution are that contains in an
\texttt{errors} hash set to provide than being included the calling side all
candidates fail execution, the voting function fails with an error that
contains all collected execution errors to provide diagnostic information for
the calling side.

>>>>

The heuristic method employed by the voting algorithm is steering the pipeline
to agree with itself – if multiple generation attempts yielded the same result,
these generation attempts are more likely to be accurate the others.

@@

Queries that fail execution are contained in an                                                                                                                                                   │ │
\texttt{errors} hash set rather than being included in voting buckets. If all                                                                                                                     │ │
candidates fail execution, the voting function fails with an error that                                                                                                                           │ │
contains all collected execution errors to provide diagnostic information to                                                                                                                      │ │
the calling side.
